Sketching for Density Estimation

### 2018-11-15 density.tex
adds sum of signed vectors and matrices

\documentclass{article} % For LaTeX2e
\usepackage{amsmath}
\usepackage[noend]{algorithmic}
\usepackage{algorithm}
\usepackage[margin=1in]{geometry}
\usepackage{xcolor}
\usepackage{amsfonts}

%\newtheorem{theorem}{Theorem}[section]
%\newtheorem{claim}[theorem]{Claim}
%\newtheorem{lemma}[theorem]{Lemma}
%\newtheorem{remark}[theorem]{Remark}
%\newtheorem{definition}[theorem]{Definition}
%\newtheorem{observation}[theorem]{Observation}
%\newtheorem{corollary}[theorem]{Corollary}
%\newtheorem{proposition}[theorem]{Proposition}
%\newtheorem{fact}[theorem]{Fact}

@@

\newcommand{\ip}[1]{\left \langle #1 \right \rangle}
\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\D}{\rho}
\newcommand{\eps}{\epsilon}
%\usepackage{ntheorem}
%\usepackage{amsthm}

%\newtheorem*{definition*}{Definition}
\newtheorem{definition}{Definition}
\newtheorem{claim}{Claim}

@@

>>>>

\documentclass{article} % For LaTeX2e
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage[noend]{algorithmic}
\usepackage{algorithm}
\usepackage[margin=1in]{geometry}
\usepackage{xcolor}
\usepackage{amsfonts}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{conjecture}{Conjecture}[section]
%\newtheorem{claim}[theorem]{Claim}
%\newtheorem{lemma}[theorem]{Lemma}
%\newtheorem{remark}[theorem]{Remark}
%\newtheorem{definition}[theorem]{Definition}
%\newtheorem{observation}[theorem]{Observation}
%\newtheorem{corollary}[theorem]{Corollary}
%\newtheorem{proposition}[theorem]{Proposition}
%\newtheorem{fact}[theorem]{Fact}

@@

\newcommand{\ip}[1]{\left \langle #1 \right \rangle}
\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\D}{\rho}
\newcommand{\eps}{\epsilon}
%\usepackage{ntheorem}

%\newtheorem*{definition*}{Definition}
\newtheorem{definition}{Definition}
\newtheorem{claim}{Claim}
%\newtheorem{theorem}{Theorem}

@@

\section{Appendix 1}
For completeness we recap a result from \cite{barany2008}.
\begin{theorem}[Simplified from B\'ar\'any \cite{barany2008} Theorem 4.1]
For any set of vector $x_1,...,x_n$ in $\R^d$ such that $\|x_i\| \le 1$ there exists a set of signs $s_1,...,s_n$ such that $||\sum_i s_i x_i || \le \sqrt{d}$.
\end{theorem}
\begin{proof}
Consider the feasible region for $\sum_i \alpha_i x_i = 0$ and all $\alpha_i \in [-1,1]$.
This feasible region is not empty because it contains the origin. 
Consider an extreme point $\alpha^*_i$ and set $s_i = 1$ w.p.\ $(1+\alpha^*_i)/2$ and $s_i = -1$ w.p.\ $(1+\alpha^*_i)/2$.
$$
\E[\|\sum s_i x_i\|^2] =  \E[\|\sum (s_i - \alpha^*_i) x_i\|^2] = \sum \E[(s_i - \alpha^*_i)^2] \|x_i\|^2= \sum (1-(\alpha_i^*)^2) \le d
$$
The last inequality holds because the values $\alpha^*_i$ are non-integer in at most $d$ places. 
Assuming otherwise would entail more than $d$ linearly independent vectors in $\R^d$ due to $\alpha^*$ being an extreme point.
\end{proof}

\noindent The conjectures appear to be provable in almost exactly the same manner
\begin{conjecture}
For any set of matrices $X_1,...,X_n$ in $\R^{d_1 \times d_2}$ such that $\|X_i\|_{2,F} \le 1$ there exists a set of signs $s_1,...,s_n$ such that $||\sum_i s_i X_i||_{2,F} \le O(\sqrt{d_1d_2\log(d_1 + d_2) })$.
\end{conjecture}
\begin{conjecture}
For any set of vector $x_1,...,x_n$ in $\R^d$ such that $\|x_i\| \le 1$ there exists a set of 
signs $s_1,...,s_n$ such that $||\sum_i s_i x_i x^T||_2 \le d\sqrt{\log{d}}$.
Here, $\|\cdot\|_2$ denotes the spectral norm of a matrix. \el{This us weak. It really should be $\sqrt{d}$ or at most $\sqrt{d\log{d}}$ }
\end{conjecture}
